Fast Bayesian Inference for Exoplanet Discovery in Radial Velocity Data

### 2014-12-15 Paper/ms.tex
Priors editing

All of the model assumptions are specified in detail in
Table~\ref{tab:priors}. Most of these priors were chosen to represent vague
prior knowledge, rather than the judgement of an informed expert on extrasolar
planets.

Cauchy distributions were used when there is a
preferred value, but since these have very heavy tails, the assumption is
quite fail safe. For example, the prior for $\mu_P$, the typical orbital period,
is centered around 1 year.

>>>>

All of the model assumptions are specified in detail in
Table~\ref{tab:priors}. Most of these priors were chosen to represent vague
prior knowledge, rather than the judgement of an informed expert on extrasolar
planets. Uniform distributions were used for parameters such as phases, where
time-translation symmetry seems plausible.
Truncated Cauchy distributions were used when there is a
preferred value, but since these have very heavy tails, the assumption is
quite fail safe relative to other possible assignments such as normal distributions.
For example, the prior for $\mu_P$, the typical orbital period,
is centered around 1 year but could be as low as $\approx e^{-21}$ years or as high
as $\approx e^{21}$ years, a very wide range. Truncation intervals are
specified with the $T(a,b)$ notation in Table~\ref{tab:priors}.
